### 2023-02-03 manuscript.tex
Revert "UoM thesis template from https://github.com/Non-Invasive-Bioelectronics-Lab/uom_thesis_template" [ci skip]
This build is based on
https://github.com/stain/2022-fdo-paper/commit/add3947b9250886170d178ca451b7469ea5fd0fe.

This commit was created by the following CI build and job:
https://github.com/stain/2022-fdo-paper/commit/add3947b9250886170d178ca451b7469ea5fd0fe/checks
https://github.com/stain/2022-fdo-paper/actions/runs/4082422816

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/d60e53cb0e45701fd619b51499c45a63f889736e/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/d60e53cb0e45701fd619b51499c45a63f889736e}{stain/2022-fdo-paper@d60e53c}
on February 3, 2023.

>>>>

This manuscript
(\href{https://stain.github.io/2022-fdo-paper/v/add3947b9250886170d178ca451b7469ea5fd0fe/}{permalink})
was automatically generated
from \href{https://github.com/stain/2022-fdo-paper/tree/add3947b9250886170d178ca451b7469ea5fd0fe}{stain/2022-fdo-paper@add3947}
on February 3, 2023.
